### 2019-03-07 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
An even older reference for the Generalized Likelihood Ratio test.

Generalized Likelihood Ratio tests date back to the seminal work of \cite{barnard1959control} and were for instance studied for change-point detection by \cite{siegmund1995using}. Exploiting the fact that bounded distribution are $(1/4)$-sub Gaussian (\ie, their moment generating function is dominated by that of a Gaussian distribution with the same mean and a variance $1/4$), the (Gaussian) GLRT, recently studied in depth by \cite{Maillard2018GLR}, can be use for our problem. We propose instead to exploit the fact that bounded distributions are also dominated by Bernoulli distributions.
We call a \emph{sub-Bernoulli distribution} any distribution $\nu$ that satisfies
$\ln \bE_{X\sim\nu}\left[e^{\lambda X}\right] \leq \phi_{\mu}(\lambda)$ with $\mu=\bE_{X\sim \nu}[X]$ and $\phi_{\mu}(\lambda) = \ln(1-\mu + \mu e^\lambda)$ is the log moment generating function of a Bernoulli distribution with mean $\mu$. Lemma 1 of \cite{KLUCBJournal} establishes that any bounded distribution supported in $[0,1]$ is a sub-Bernoulli distribution.

>>>>

Generalized Likelihood Ratio tests date back to the seminal work of \cite{Wilks1938}, and were for instance studied for change-point detection by \cite{barnard1959control,siegmund1995using}. Exploiting the fact that bounded distribution are $(1/4)$-sub Gaussian (\ie, their moment generating function is dominated by that of a Gaussian distribution with the same mean and a variance $1/4$), the (Gaussian) GLRT, recently studied in depth by \cite{Maillard2018GLR}, can be use for our problem. We propose instead to exploit the fact that bounded distributions are also dominated by Bernoulli distributions.
We call a \emph{sub-Bernoulli distribution} any distribution $\nu$ that satisfies
$\ln \bE_{X\sim\nu}\left[e^{\lambda X}\right] \leq \phi_{\mu}(\lambda)$ with $\mu=\bE_{X\sim \nu}[X]$ and $\phi_{\mu}(\lambda) = \ln(1-\mu + \mu e^\lambda)$ is the log moment generating function of a Bernoulli distribution with mean $\mu$. Lemma 1 of \cite{KLUCBJournal} establishes that any bounded distribution supported in $[0,1]$ is a sub-Bernoulli distribution.
